---
title: "Using clarifai"
author: "Gaurav Sood"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using clarifai}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Installation

To get the current development version from GitHub:

```{r install, eval=F}
# install.packages("devtools")
devtools::install_github("soodoku/clarifai")
```

#### Load up the lib:
```{r load_lib}
library(clarifai)
```

#### Authentication

Start by setting Client ID and secret, which you can get from [https://developer.clarifai.com/](https://developer.clarifai.com/)
```{r, eval=FALSE}
secret_id(c("client_id", "secret"))
```

Next, get the token (the function also sets it):
```{r, eval=FALSE}
get_token()
```

#### Get Information

Get information about your application:
```{r}
get_info()
```

#### Get Tags

We are now all set. Let's play. Get tags of a remote image:

```{r}
res <- tag_image_urls("http://www.clarifai.com/img/metro-north.jpg")
```

Get tags for a local image:
```{r, eval=F}
path <- system.file("inst/extdata/", package = "clarifai")
filep <- paste0(path, "/metro-north.jpg")
tag_images(filep)
```

Provide feedback about tags for an image, including suggesting new tags, suggesting that some tags be removed etc. 

#### Provide Feedback

```{r feedback, eval=FALSE}
feedback(file_path="path_to_image", feedback_type="add_tags", feedback_value="suggested_tag")

## $status_code
## [1] "OK"

## $status_msg
## [1] "Feedback successfully recorded. "
```